Depletion capabilities in the OpenMC Monte Carlo particle transport code

### 2020-05-03 manuscript.tex
One more reference

Lots of community efforts toward coupled transport-depletion calculations with
OpenMC~\citep{gul2017ane,lanversin2017icone,lanversin2019phd,liu2019nst,zhuang2020pne,zhao2020ned,zhang2020ane}.

>>>>

Lots of community efforts toward coupled transport-depletion calculations with
OpenMC~\citep{gul2017ane,lanversin2017icone,lanversin2019phd,liu2019nst,zhuang2020pne,zhao2020ned,zhao2020cpc,zhang2020ane}.
